---
title: "Citibike_ML"
author: "Hongyang Yang"
date: "12/4/2017"
output:
  pdf_document: default
  html_document: default
---

# Purpose: Is there a linear relationship bewteen the number of rents per day and the weather data in NYC? Which weather factor affect the number of rents the most?
```{r,warning=FALSE}
library(ggplot2)
library(glmnet)
library(ISLR)
library(tree)
library(randomForest)
library(e1071)
library(MASS)
library(caret)
library(gbm)

citibike_daily_weather=read.csv("citibike_daily_weather.csv")

sum(is.na(citibike_daily_weather))
citibike_daily_weather=na.omit(citibike_daily_weather)

set.seed(1)
train_ind=sample(1:nrow(citibike_daily_weather),0.7*nrow(citibike_daily_weather))
train=citibike_daily_weather[train_ind,c(2,5:14)]
test=citibike_daily_weather[-train_ind,c(2,5:14)]

test_x=test[,-1]
test_y=test[,1]

```

# Model 1: Linear Regression
```{r,warning=FALSE}
###################################
#######Linear Regression##########
###################################

linear_model=lm(RENT~.,data=train)
summary(linear_model)
linear_pre_y=predict(linear_model,test_x)
p.linear<-qplot((linear_pre_y), (test_y), xlab='Predicted #RENT per day', 
              ylab='Actual #RENT per day', main='Linear Regression')
p.linear + geom_abline(slope=1, intercept=0)



```





# Model 2: Random Forest


```{r,warning=FALSE}

library(randomForest)
library(e1071)
library(MASS)
library(caret)


RF_Model=randomForest(RENT~.,data = na.omit(train) ,importance=TRUE, na.rm = TRUE)

RF_Model
yhat_bag=predict(RF_Model,test_x)
MSE_RF=mean((yhat_bag-test_y)^2,na.rm=TRUE)


#running the result
p.rf<-qplot((yhat_bag), (test_y), xlab='Predicted #RENT per day', 
            ylab='Actual #RENT per day', main='Random Forest')
p.rf + geom_abline(slope=1, intercept=0)


plot(RF_Model, log="y")
varImpPlot(RF_Model,main='Random Forest Importance Table')
varImp(RF_Model)


```

# Model 3: GBM

```{r,warning=FALSE}


#Generalized Boosted Regression Modeling
library(gbm)
gbm_model=gbm(RENT~.,data = train,dist="gaussian",n.tree = 400,shrinkage=0.1, cv.folds = 5)

best.iter <- gbm.perf(gbm_model,method="OOB")


gbm.perf(gbm_model,method="OOB")
print(best.iter)

best.iter <- gbm.perf(gbm_model,method="cv")
print(best.iter)
gbm.perf(gbm_model,method="cv")


sumary_GBM=summary(gbm_model)
sumary_GBM

gbm_pred_y = predict(gbm_model, test, n.tree = 400, type = 'response')
MSE_gbm=mean((gbm_pred_y-test_y)^2,na.rm=TRUE)

p.rf<-qplot((gbm_pred_y), (test_y), xlab='Predicted #RENT per day', 
            ylab='Actual #RENT per day', main='Generalized Boosted Regression')
p.rf +  geom_abline(slope=1, intercept=0)





```
# Model 4: Regression Tree

```{r,warning=FALSE}
library(ISLR)
library(tree)
#set.seed(1)
tree_model=tree(RENT~.,data=train)
plot(tree_model)
text(tree_model,pretty=1)

tree_pred_y=predict(tree_model, test_x)

MSE_tree=mean((test_y-tree_pred_y)^2,na.rm=TRUE)


MSE_tree


##### CROSS VALIDATION #####
cv_model=cv.tree(tree_model)  
plot(cv_model$size,cv_model$dev,type='b')
bestSize=which.min(cv_model$dev)
print(bestSize)
# Prune Tree
prune.tree=prune.tree(tree_model,best=2)  
plot(prune.tree)
text(prune.tree,pretty=0)
pred.prune.tree = predict(prune.tree, newdata=test)
MSE_prune_tree=mean((test_y-pred.prune.tree)^2) 
MSE_prune_tree


```

# Conclusion: Based on the 5 models we have, it can be concluded that there is a linear relationship between the number of rents per day and the weather data in NYC.